---
title: "Sweden Solar System"
author: "Peter"
date: "10/9/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(leaflet)
```

## Solar system in Sweden

The Sweden Solar System is the world's largest permanent scale model of the Solar System. The Sun is represented by the Ericsson Globe in Stockholm, the largest hemispherical building in the world. The inner planets can also be found in Stockholm but the outer planets are situated northward in other cities along the Baltic Sea. The system was started by Nils Brenning and Gosta Gahm and is on the scale of 1:20 million.

```{r}
locations <- data.frame(
  lat = c(59.293583, 59.319706, 59.352750, 59.368808, 59.398252, 59.649482), 
  lng = c(18.083571, 18.070924, 18.058432, 18.053378, 18.036139, 17.923427)
  )
link <- c(
  "<a href='https://en.wikipedia.org/wiki/Ericsson_Globe'>Sun: Ericsson Globe</a>",
  "<a href='https://en.wikipedia.org/wiki/Stockholm_City_Museum'>Mercury: Stockholm City Museum</a>",
  "<a href='http://www.vetenskapenshus.se'>Venus: Museum of Natural History</a>",
  "<a href='http://www.nrm.se'>Earth and Moon: Museum of Natural History</a>",
  "<a href='https://en.wikipedia.org/wiki/M%C3%B6rby_Centrum'>Mars: M??rby Centrum in Danderyd</a>",
  "<a href='https://en.wikipedia.org/wiki/Stockholm_Arlanda_Airport'>Jupiter: Arlanda Airport</a>"
  )
locations %>% leaflet() %>% addTiles() %>% addMarkers(popup = link)
```



